Cross Validation Analysis

### 2023-06-26 minos/validation/cross_validation.Rmd
Transformed hh_income with inverse hyperbolic sine for plotting. Added a package to the environment as part of this

require(tidyverse)
require(ggplot2)
require(here)

@@

NOTE: LOG SCALE!

@@

ggplot(snap, aes(x = observed, y = predicted)) +
  geom_point() +
  geom_abline(slope=1, intercept=0) +
  facet_wrap(~time) +
  labs(title = 'hh_income observed vs predicted')

@@

ggplot(filter(snap, time == 2014), aes(x = observed, y = predicted)) +
  geom_point() +
  geom_abline(slope=1, intercept=0) +
  stat_ellipse(color='green') +
  labs(title = 'SF_12 : 2014')

ggplot(filter(snap, time == 2016), aes(x = observed, y = predicted)) +
  geom_point() +
  geom_abline(slope=1, intercept=0) +
  stat_ellipse(color='green') +
  labs(title = 'SF_12 : 2016')

ggplot(filter(snap, time == 2018), aes(x = observed, y = predicted)) +
  geom_point() +
  geom_abline(slope=1, intercept=0) +
  labs(title = 'SF_12 : 2018')

ggplot(filter(snap, time == 2020), aes(x = observed, y = predicted)) +
  geom_point() +
  geom_abline(slope=1, intercept=0) +
  labs(title = 'SF_12 : 2020')

ggplot(snap, aes(x = observed, y = predicted, group = time, color = time, shape = time)) +
  geom_point(size = 1) +
  geom_abline(slope=1, intercept=0) +
  labs(title = 'SF_12')

>>>>

require(tidyverse)
require(ggplot2)
require(here)
require(scales)

@@

@@

asinh_trans <- scales::trans_new(
  "inverse_hyperbolic_sine",
  transform = function(x) {asinh(x)},
  inverse = function(x) {sinh(x)}
)

ggplot(snap, aes(x = observed, y = predicted)) +
  geom_point() +
  scale_y_continuous(trans=asinh_trans) +
  scale_x_continuous(trans=asinh_trans) +
  geom_abline(slope=1, intercept=0) +
  stat_ellipse(color='red') +
  facet_wrap(~time) +
  labs(title = 'hh_income observed vs predicted',
       subtitle = 'inverse hyperbolic sine transformation')

@@

ggplot(snap, aes(x = observed, y = predicted, group = time)) +
  geom_point(size = 1) +
  geom_abline(slope=1, intercept=0) +
  stat_ellipse(color='red') +
  facet_wrap(~time) +
  labs(title = 'SF_12')
